Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-04 paper/ms.tex
Add caption to cluster offset fig

\begin{figure}
\plotone{fig/cluster_offset.pdf}
\caption{Caption.}
\label{fig:cluster_offset}
\end{figure}

>>>>

\begin{figure}
\plotone{fig/cluster_offset.pdf}
\caption{The $z$ offset necessary in order for the action error induced by our
midplane effect to be comparable to the intrinsic action dispersion from a
cluster of mass $m_c$. We compute the intrinsic dispersion from
Equation~\ref{eq:action_disp} and convert the dispersion to a $z$ offset using
the result from Figure~\ref{fig:many_orbit_wrong_ref}. We consider the result
for three different orbits with varying vertical actions of $J_z = 0.7, 7.0,
22.9\,\actunit$ ($z_{\text{max}} = 122,425,854\,\pc$) --- colored by
\Gus{blue, orange, red}, respectively. Nearby open clusters have actions
closest to the $J_z=0.7\,\actunit$ (blue) orbit, see Table~\Gus{x}.}
\label{fig:cluster_offset}
\end{figure}
